FraCaS: Temporal Analysis

### 2020-04-23 paper2020/paper.tex
wibble
failed attempt to include bibliography
notes

\title{FraCaS: Temporal Analysis}
\author{Jean-Philippe Bernardy \qquad Stergios Chatzikyriakidis \\
  University of Gothenburg\\
  {\tt firstname.lastname@@gu.se} \\}

@@

\section{Introduction}
Stergios
\section{Background}
\paragraph{GF}
If needed
\paragraph{Coq}
If needed
\paragraph{Temporal Semantics}
Stergios

@@

(The difference between actitivty and achievement is that for the
latter time intervals can be assumed to be of nil duration. However
this appears to play little role, if any, in our analysis.)

@@

Indeed, from \textbf{P3} we get that Smith was in paris between May
5th and May 15th. Because being in Paris is stative, we also get that
Smith was in Paris in any subinterval. Contrary to unicity of action,
subsumption is always valid.

@@

>>>>

\title{FraCaS: Temporal Analysis}
\author{Jean-Philippe Bernardy \qquad Stergios Chatzikyriakidis \\
  University of Gothenburg\\
  {\tt firstname.lastname@gu.se} \\}

@@

\section{Introduction}
Stergios

We do not care about classifying sentences as felicitous/infelicitous
or grammatical/ungrammatical, rather we assume that the sentence is
correct and care about giving it an appropriate interpretation as a
logical formula.  Indeed, our evaluation uses entailment properties
only.

\section{Background}
\paragraph{GF}
If needed
\paragraph{Coq}
If needed
\paragraph{Temporal Semantics}
Stergios

We use notions of ``stative'', ``achievement'', ``activity''. Our
definition do not seem to match perfectly the definitions found in the
literature; however we think they are good definitions, given that
they generally afford the correct inferences for the testsuite. (We
assume the testsuite is correct.)

@@

(The difference between actitivty and achievement is that for the
latter time intervals can be assumed to be of nil\footnote{TODO: needs qualification} duration. However
this appears to play little role, if any, in our analysis.)

@@

Indeed, from \textbf{P3} we get that Smith was in paris between May
5th and May 15th. Because "being in Paris" is stative, we also get that
Smith was in Paris in any subinterval. Contrary to unicity of action,
subsumption is always valid.

@@

% \bibliography{../PaperTools/bibtex/jp}
